Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-02-25 NEUROC/Response-MinorRev/response_letter-minor-rev.tex

% !TEX program=xelatex
% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.

\documentclass[12pt]{article}
\usepackage{fontspec} % For loading fonts
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{float}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{soul}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=black]{hyperref}
\usepackage{natbib}
\setmainfont{Times New Roman}
% Vector
\newcommand{\MyVec}[1]{\boldsymbol{#1}}
% Matrix
\newcommand{\MyMat}[1]{\boldsymbol{#1}}
% Vectors with hat
\newcommand{\hvec}[1]{\hat{\boldsymbol{h}}_{#1}}
% Model parameters
\newcommand{\Param}[1]{\textcolor{blue}{#1}}

@@

\section*{Response to the Reviewers}
% General intro text goes here
We thank the reviewers for their insightful comments on our work.
%
We have made modifications to our manuscript according to Reviewer 1's comments.

% Let's start point-by-point with Reviewer 1
\reviewersection

% R1Q0
\begin{point}
    In the revised manuscript, the authors have addressed all my concerns, especially adding more computation efficiency discussion. Current version looks very impressive. Just a small issue left. Some discussions about limitations or future efforts should be better added.
\end{point}

\begin{reply}
    Thank you for the insightful suggesion.
    %
    According to the suggestion, we have added a paragraph at the end of Section 7 ``Conclusion and Future Work'' to discuss the limitations of our work and point out potential future research directions.
    %
    Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the single-GPU environment on static graphs with the message-passing framework.
    %
    In fact, performance bottlenecks of GNN training/inference over the multi-GPU or distributed environment, dynamic graphs and other GNN frameworks are also worth studying.
    %
    In the future, we plan to explore the GNN training/inference performance analysis under the following scenarios:
    %
\begin{enumerate}
    \item \emph{Multi-GPU or distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, training/inferring GNNs with the multi-GPU environment or the distributed environment is essential.
    %
    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to study.

    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs usually have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting [\cite{li2018_DCRNN}] and human action recognition [\cite{yan2018_STGCN}].
    %
    Many new GNNs are proposed to handle this kind of dynamic graphs.
    %
    The differences of performance issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.

    \item \emph{Emerging GNN frameworks.}
    %
    In this work, we analyzed the widely-used message-passing framework in GNN learning systems.
    %
    However, some emerging GNN learning systems adopt different frameworks like SAGA framework [\cite{ma2019_neugraph}].
    %
    It is interesting to research whether different frameworks would lead to different performance bottlenecks.
\end{enumerate}

\end{reply}

### 2021-02-25 NEUROC/sec7-conclusion.tex
更新正文内容。

Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
%
In fact, performance bottlenecks of GNN training/inference over the multi-GPU or distributed environment, dynamic graphs, and other GNN frameworks are also worth studying.
%
In the future, we plan to explore the GNN training/inference performance analysis under the following scenarios:
%
\begin{enumerate}
    \item \emph{Multi-GPU or distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, training/inferring GNNs with the multi-GPU environment or the distributed environment is essential.
    %
    Multi-GPU and distributed GNN training will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to study.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs usually have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
    %
    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
    %
    Many new GNNs are proposed to handle this kind of dynamic graph.
    %
    The differences of performance impacting issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
    %
    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
    \item \emph{Other GNN frameworks.}
    %
    In this work, we analyzed the widely-used message-passing framework in GNN learning systems.
    %
    However, some emerging GNN learning systems adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
    %
    It is interesting to research whether different frameworks would lead to different performance bottlenecks.
\end{enumerate}

@@

This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No. U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Alibaba Innovative Resarch Project, and the program B for outstanding PhD candidate of Nanjing University.

>>>>

Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the single-GPU environment on static graphs with the message-passing framework.
%
In fact, performance bottlenecks of GNN training/inference over the multi-GPU or distributed environment, dynamic graphs, and other GNN frameworks are also worth studying.
%
In the future, we plan to explore the GNN training/inference performance analysis under the following scenarios:
%
\begin{enumerate}
    \item \emph{Multi-GPU or distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, training/inferring GNNs with the multi-GPU environment or the distributed environment is essential.
    %
    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to study.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs usually have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
    %
    Many new GNNs are proposed to handle this kind of dynamic graphs.
    %
    The differences of performance issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
    %
    \item \emph{Emerging GNN frameworks.}
    %
    In this work, we analyzed the widely-used message-passing framework in GNN learning systems.
    %
    However, some emerging GNN learning systems adopt different frameworks like the SAGA framework \cite{ma2019_neugraph}.
    %
    It is interesting to research whether different frameworks would lead to different performance bottlenecks.
\end{enumerate}

@@

This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No. U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Jiangsu, China, Alibaba Innovative Research Project, and the program B for outstanding PhD candidate of Nanjing University.
